Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
排版完成

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the collection of shopping app users' purchase record data, patients' clinical data, and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} built the first FL system that is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team from WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL to some industrial cyber–physical systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{li2021flphish, ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. We have also studied the problem of Byzantine defense, and this study is the extensive version of our previous work \cite{li2021flphish}. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
\end{itemize}

@@

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks mentioned in Section III.B:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine attacker, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight). The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine attacker, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

  \subsubsection{{\textit{Experiment Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB. We implement all deep learning models using Keras\footnote{https://keras.io/}.

@@

  \subsection{Performance Comparison under Random Attacks}
  From Fig. \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine attackers as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5). Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) towards untargeted Byzantine attacks in EFL.

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine attackers are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine attackers and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine attackers during the aggregation iterations. Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine attackers. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine attackers, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine attackers can avoid being detected by FLPhish($\tau$). As the fractions of Byzantine attackers go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine attackers are.

>>>>

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. Such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the collection of shopping app users' purchase record data, patients' clinical data, and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of the `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} built the first FL system that is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team from WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL to some industrial cyber–physical systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{li2021flphish, ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers. For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value in global model updates. We have also studied the problem of Byzantine defense, and this study is the extensive version of our previous work \cite{li2021flphish}. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is more compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
\end{itemize}

@@

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks mentioned in Section III.B:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine attacker, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight). The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine attacker, it mislabels the labels to a randomly chosen label.
    \end{itemize}

  \subsubsection{{\textit{Experiment Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU. We implement all deep learning models using Keras\footnote{https://keras.io/}.

@@

  \subsection{Performance Comparison under Random Attacks}
  \par We evaluate FLPhish(weight) against random Byzantine attacks in EFL. From Fig. \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2). We refer from the result that the random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine attackers as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5). Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks.

  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) against untargeted Byzantine attacks in EFL.

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine attackers are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine attackers and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine attackers during the aggregation iterations. Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine attackers. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine attackers, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine attackers can avoid being detected by FLPhish($\tau$). As the fractions of Byzantine attackers go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine attackers are.
